Multi-period and Multi-product Batch Processing Time Maximization Problem

### 2023-07-31 multi-period/manuscript.tex
updating paper
math model

$\textrm{I}_{0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;

@@

$\textrm{I}_{id}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;

@@

\begin{equation}
P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{I}_{0} - \textrm{PO}_{i1}
\end{equation}

@@

\begin{equation}
\end{equation}

@@

\begin{equation}
UI_{id}, O_{id}, D_{id} \in  \mathbb{Z}^+ \quad \forall i,d
\end{equation}

@@

T.B. Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing. Í.R.B. Aquino: Data curation. R.C.S. Menêzes: Data curation.

>>>>

$\textrm{UI}_{i0}$ is the initial free factory storage of product $i$ on the beginning of the (\emph{first}) planning day;

@@

$\textrm{I}_{d}$ is the maximum quantity allowed for additional factory storage of all products on day $d$;

@@

\begin{equation}
P_i + UI_{i1} - D_{i1} - O_{i1} = \textrm{UI}_{i0} - \textrm{PO}_{i1}
\end{equation}

@@

\begin{equation}
I_{1} + \sum_{i}\{P_i -  D_{i1} - O_{i1}\} = \textrm{I}_{0} 
\end{equation}

\begin{equation}
I_{d} - I_{d-1} + \sum_{i}\{P_i -  D_{id} - O_{id}\} = 0 \quad \forall (d>1)
\end{equation}

@@

\begin{equation}
UI_{id}, I_{d}, O_{id}, D_{id} \in  \mathbb{Z}^+ \quad \forall i,d
\end{equation}

\begin{equation}
I_{d} \in  \mathbb{Z}^+ \quad \forall d
\end{equation}

@@

T.B. Fraga: Conceptualization, Project administration, Supervision, Software, Methodology, Validation, Formal analysis, Writing – original draft, Writing – review \& editing. Í.R.B. Aquino: Data curation.
